Parameter Estimation for the CES Model

### 2013-07-19 CES.Rnw
Now creating graphs of SSE vs. rho and rho_1 for UK CES with q.

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{language} % Obtain language.sty from https://github.com/rpruim/latex
\usepackage{underscore} % Should be part of any LaTeX distribution.

@@

This approach correctly respects the constraints, 
but the \texttt{LM} algorithm does not converge.

@@

<<>>=
modelUKQ_grid <- cesEst(data=dataUK, yName="iGDP", xNames=c("iCapStk", "iLabor", "iQ"), tName="iYear")
modelUKQ_grid <- cesEst(data=dataUK, 
                        yName="iGDP", 
                        xNames=c("iCapStk", "iLabor", "iQ"), 
                        tName="iYear",
                        method="L-BFGS-B",
                        rho=seq(from=1, to=20, by=2), 
                        rho1=seq(from=1, to=2, by=0.2))
summary(modelUKQ_grid)
@

<<>>=
plot(modelUKQ_grid)
@

>>>>

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{language} % Obtain language.sty from https://github.com/rpruim/latex
\usepackage{underscore} % Should be part of any LaTeX distribution.
\usepackage{float} % For precise figure positioning.

@@

The above approach correctly respects the constraints, 
but the \texttt{LM} algorithm does not converge.

@@

<<>>=
modelUKQ_grid <- cesEst(data=dataUK, 
                        yName="iGDP", 
                        xNames=c("iCapStk", "iLabor", "iQ"), 
                        tName="iYear",
                        method="L-BFGS-B",
                        rho=seq(from=5, to=30, by=5), 
                        rho1=seq(from=-0.5, to=1.5, by=0.5))
summary(modelUKQ_grid)
@

The negative of the $SSE$ values from the grid search can be plotted as a function of 
$\rho$ and $\rho_1$ quite easily, as shown in Figure~\ref{fig:UKQ-grid-coarse}.
The \texttt{plot} function puts the negative of $SSE$ on the $z$ axis, 
so better curve fits appear as higher on the $z$ axis of this plot.

<<UKQ-grid-coarse, fig.pos="H", fig.cap="$-SSE$ vs. $\\rho$ and $\\rho_1$. Coarse grid.">>=
plot(modelUKQ_grid)
@

To explore the details at high values of $\rho$ and values of 
$\rho_1 \rightarrow -1$, we can do a detailed analysis\dots

<<>>=
modelUKQ_grid_detail <- cesEst(data=dataUK, 
                        yName="iGDP", 
                        xNames=c("iCapStk", "iLabor", "iQ"), 
                        tName="iYear",
                        method="L-BFGS-B",
                        rho=seq(from=14, to=20, by=1), 
                        rho1=seq(from=-0.95, to=-0.5, by=0.05))
summary(modelUKQ_grid_detail)
@

{\dots}and build a graph as shown in Figure~\ref{fig:UKQ-grid-fine}.

<<UKQ-grid-fine, fig.pos="H", fig.cap="$-SSE$ vs. $\\rho$ and $\\rho_1$. Fine grid.">>=
plot(modelUKQ_grid_detail)
@

The best fit for the UK appears to be $\rho_1 \rightarrow -1$ ($\sigma_1 \rightarrow \infty$, meaning perfect subsitutibility between $k$ and $l$). It is unclear why there is a sudden dropoff in $-SSE$ at larger values of $\rho$.
